Robust Winner Determination and Simultaneous Elicitation of Scoring Rules and Preferences

### 2019-02-20 draft.tex
Given up alt def PMR

We formalize the notion of minimax regret in multiple steps.
First of all, denote by $s^*_{\profile, \w} = \max_{y \in A} s(y; \profile, \w)$ the score achieved by winning alternatives under $\profile$ and using weights $\w$. Now define $\Regret(x, \profile, \w)$ as the “regret” of selecting $x$ as a winner instead of choosing the optimal alternative under $\profile$ and $\w$:
\[\Regret(x, \profile, \w) = s^*_{\profile, \w} - s(x; \profile, \w).\]

%The pairwise max regret $\PMR(x,y;\pprofile,W)$ of $x$ relative to $y$ given partial profile $\pprofile$ and the set of weights $W$
%is the worst-case loss under all possible realizations of the full profile {\em and} all possible instantiations of the weights:
%\begin{align}
%\PMR(x,y; \pprofile, W) & = \max_{\w \in W} \max_{\profile \in C(\pprofile)} s(y; \profile,\w) - s(x; \profile,\w).
%\end{align}

>>>>

We formalize the notion of minimax regret in multiple steps.
First of all, $\Regret(x, \profile, \w)$ is the “regret” of selecting $x$ as a winner instead of choosing the optimal alternative under $\profile$ and $\w$:
\[\Regret(x, \profile, \w) = \max_{y \in A} s(y; \profile,\w) - s(x; \profile, \w).\]

The pairwise max regret $\PMR(x,y;\pprofile,W)$ of $x$ relative to $y$ given partial profile $\pprofile$ and the set of weights $W$
is the worst-case loss under all possible realizations of the full profile {\em and} all possible instantiations of the weights:
\begin{align}
\PMR(x,y; \pprofile, W) & = \max_{\w \in W} \max_{\profile \in C(\pprofile)} s(y; \profile,\w) - s(x; \profile,\w).
\end{align}
